### 2021-09-29 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betadiversity_response@47163354c060412ccb1b62ee807bba3ef6e0340f 🚀

Yet, the precise meaning of \(\beta_{st}\), namely the importance of
species turnover in the overall dissimilarity, has been difficult to
capture, and a source of confusion for some practitioners. This is not
particularly surprising, as this component of the decomposition responds
to unique species introducing their unique interactions both between
themselves, and with species that are common to both networks
fig.~\ref{fig:concptual}. For this reason, it is important to come up
with guidelines for the interpretation of this measure, and how to use
it to extract ecological insights.

>>>>

Yet, the precise meaning of \(\beta_{st}\), namely the importance of
species turnover in the overall dissimilarity, has been difficult to
capture, and a source of confusion for some practitioners. This is not
particularly surprising, as this component of the decomposition responds
to unique species introducing their unique interactions both between
themselves, and with species that are common to both networks
fig.~\ref{fig:conceptual}. For this reason, it is important to come up
with guidelines for the interpretation of this measure, and how to use
it to extract ecological insights.
